A scenario for a Planckian standard kilogram

### 2017-11-30 manuscript_gravitationalconstant.tex
some words on low-Earth orbits

We are not supposing the measurement of the gravitational constant 
using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could be part of 
a spacecraft reaching a Lagrange point. But our estimates suggest that this approach to increase the precision of the gravitational constant should be taken seriously.

>>>>

We have not attempted in this paper to consider the cost of such an
experiment.  A mission to an Earth-Sun $L_4$ or $L_5$ with
liquid-helium cryogenics would obviously be very expensive, and also
carry an enhanced risk of unrepairable malfunctions killing the
experiment.  If the goals could be achieved in low-Earth orbit, the
prospects would be much more realistic.  The difficulty in low-Earth
orbit is that tidal acceleration due to the Earth would become
comparable to the two-body gravitational acceleration, with the Moon
and Sun also tidally perturbing the system.  The two-body system would
have a complicated orbit, very different from the nearly circular
orbit we have considered, and the initial conditions would have to be
chosen so as to avoid chaotic orbits.  Whether a sufficiently detailed
model for the tidal acceleration could be constructed and fitted to
the two-body orbital data is an open question.
